---
title: "Untitled"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(rgbif)
library(finch) # for dwca
library(here)
```


# Data from MIGRAME 
Acceder al conjunto de datos MIGRAME
https://www.gbif.org/dataset/6c6a9003-ecea-4f3a-9f2f-414107da65c1 



```{r}
# mig <- occ_download_datasets(key = "6c6a9003-ecea-4f3a-9f2f-414107da65c1") 
 
# Download the dwca zip file and process it 
# Read the dataset 
mig_dwca <- dwca_read(here::here("raw_data/dwca-migrame-v1.8.zip"), read = TRUE)

# Get occurrences and measurementOrFact files 
mig_occ <- mig_dwca$data[["occurrence.txt"]]
mig_mof <- mig_dwca$data[["measurementorfact.txt"]]
```

# Prepare data 
```{r}
aux_occ <- mig_occ %>% 
  dplyr::select(id, date = eventDate, sp = scientificName, lat = decimalLatitude, long = decimalLongitude)

# Prepare measurement of fact dataframe 
aux_mof <- mig_mof %>% 
  dplyr::select(id, measurementType, measurementValue) %>% 
  spread(measurementType, measurementValue)
  
# Join data
df_occ <- aux_occ %>% 
  inner_join(aux_mof, by="id") %>% 
  rename(diam = `diameter size`, height = `tree height`) %>% 
  mutate(id_transect =
           str_remove(
             str_replace(id, pattern = "urn:catalog:OBSNEV:MIGRAME:MIG-", ""),
             "-.*"), 
         id = as.numeric(str_sub(id, start=-5)))

# Change name of species 
df_occ <- df_occ %>% 
  mutate(sp = recode(sp, 
         `Acer opalus subsp. granatense (Boiss.) Font Quer & Rothm.` = "Aop", 
         `Juniperus communis Thunb.` = "Jco",
         `Quercus pyrenaica Willd.` = "Qpy",
         `Pinus sylvestris Lour.` = "Psy",
         `Quercus ilex L. subsp. ballota` = "Qil",
         `Sorbus aria Wimm. ex Nyman` = "Sar"))

```

```{r}
# Get transect data and join
# Transect data comes from Supplementary of https://doi.org/10.3897/phytokeys.56.5482 

# Table S1. Information about transects of the project. Elevation in m a.s.l.. 
# Type: AM = Altitudinal migration; FO = Forest; MH = Marginal Habitat. 
# Subtype: 
#   AC-e = Abandoned Cropland: edge; AC-i = Abandoned Cropland: inside; 
#   Pp-e = Pine plantations: edge; Pp-i: Pine plantations: inside; 
#   TE = Treeline Ecotone. 
# Locality: CA = Robledal de Cáñar; SJ = Robledal de San Juan. 

mig_transect <- read_csv(here::here("raw_data/mig_transect.csv")) %>% 
  dplyr::select(id_transect = `Transect name`, elev = Elevation, 
                type = Type, subtype = Subtype, loc = Locality) 


df_occ <- df_occ %>% inner_join(mig_transect, by="id_transect") 
```


# Select forest plots 

```{r}
df <- df_occ %>% filter(type == "FO")
```


```{r}
x <- df_occ %>% filter(sp == "Qpy") %>% 
  mutate(h = height/100) %>% 
  rename(d = diam) %>% 
  mutate(w = ifelse(d > 7,  
              0.0261* d^2 * h,
              ifelse(d < 2,
                     (0.898*d) - (0.445*h), 
              (-0.0260 * d^2) + (0.536 * h) + (0.000538 * d^2 * h)      
                     )),
  wr = 0.143*d^2) %>% 
  filter(type == "FO") %>% 
  dplyr::select(-height, -type, -subtype) %>% 
  write_csv(path = "/Users/ajpelu/Google Drive/Almacen_Antonio/CURSOS/IMPARTIDOS/2019_CURSO_Estadistica_OAPN/curso_analisis_oapn/biomass_pyrenaica.csv")



```


```{r}

df_occ %>% filter(sp == "Qpy") %>% 
  filter(diam > 7.5) %>% 
  ggplot(aes(x=diam, y=height, colour = loc)) + geom_point() +
  geom_smooth() + 
  theme_bw()

```

```{r}
## TODO improve function to compute BIOMASS 

# w (kg); diam (cm); h (m) 
w_sb7 <- (0.0261* d^2 * h)
w_b27 <- (-0.0260 * d^2) + (0.536 * h) + (0.000538 * d^2 * h)
w_b2 <- (0.898*d) - (0.445*h)
w_r <- 0.143*d^2



head(df) 

a <- df %>% filter(diam < 2 & height == 85)
b <- df %>% filter(diam > 2 & diam <= 7) %>% 
  filter(height  == 190)
c <- df %>% filter(diam > 7 & height == 1350)

x <- a %>% bind_rows(b,c)


biomassQpy <- function(d, h, ...){
  
  if (d > 7) {
    w <- (0.0261* d^2 * h)
    } else if (d < 2) {
    w <- (0.898*d) - (0.445*h)
    } else { 
    w <- (-0.0260 * d^2) + (0.536 * h) + (0.000538 * d^2 * h)
    }
  w
  }

biomassQpy_vec <- Vectorize(biomassQpy, vectorize.args = c("d","h"))



xw <- x %>% mutate(h = height/100) %>% 
  rename(d = diam) %>% 
  mutate(
  w = ifelse(d > 7,  
              0.0261* d^2 * h,
              ifelse(d < 2,
                     (0.898*d) - (0.445*h), 
              (-0.0260 * d^2) + (0.536 * h) + (0.000538 * d^2 * h)      
                     )),
  wr = 0.143*d^2) %>% 
  mutate(
    wf = biomassQpy_vec(d, h)
  )
    
  
```


```{r}
df_biomass <- df %>% mutate(h = height/100) %>% 
  rename(d = diam) %>% 
  mutate(w = ifelse(d > 7,  
              0.0261* d^2 * h,
              ifelse(d < 2,
                     (0.898*d) - (0.445*h), 
              (-0.0260 * d^2) + (0.536 * h) + (0.000538 * d^2 * h)      
                     )),
  wr = 0.143*d^2)
```






# Mas datos
IFN 
[X] MIGRAME
Dendro 

OBSNEV 
?? SINFONEVADA

[ ] Alvaro Rubio San Jerónimo? 
[ ] 

[ ] Camarate?? 
* [X] San Juan

    - [X] MIGRAME
    - [X] DENDRO 
    - [ ]

* [ ] San Jerónimo 
* [ ] Dilar 
* [ ] Durcal
* [ ] Cañar

    - [X] MIGRAME
    - [X] DENDRO 
    - [ ]

[ ] Pórtugos 
[ ] Busquistar










```{r}
# Access data of Wood density
library(BIOMASS)

wdqp <- wdData %>% 
  filter(genus == "Quercus" & species == "pyrenaica") %>% 

# Gutierrez Oliva, A. and Plaza Pulgar, F. 1967. Caracteristicas fisico-mecanicas de las maderas espanolas. Ministerio de Agricultura, Direccion general de montes, caza y pesca fluvial, Instituto Forestal de Investigaciones y Experiencias. Madrid. 10 3 pp., A. and Plaza Pulgar, F. 1967. 
```






```





```{r}
head(df_occ)

# Filter species (only Q. p)
df_occ %>% 
  filter(sp == "Quercus pyrenaica Willd.") %>% 
  filter(diam > 7.5) %>% 
  ggplot(aes(x=diam, y=height)) + geom_point(col="black", alpha=.8) +
  geom_smooth(method = "lm", colour="red") + 
  theme_bw()

```











