---
title: "Estimate height"
output: pdf_document
bibliography: ../references.bib
editor_options: 
  chunk_output_type: console
---

```{r, message=FALSE, warning=FALSE}
source(here::here("load_pkgs.R"))
```

## Explore data 
```{r}
tree <- read_csv(here::here("data/tree_data.csv"), col_types = cols())

tree %>% group_by(sp) %>% 
  count(is.na(h)) %>% 
  spread(`is.na(h)`, n) %>% 
  rename(n=`FALSE`, n_na = `TRUE`) %>% 
  knitr::kable() 
```

Trees with no values for height belongs to *Q. ilex* and *Q. pyrenaica*. Height data for computation of *Q. ilex* biomass is not needed according to allometric equation proposed by @RuizPeinadoetal2012BiomassModels. For *Q. pyrenaica* and estimation of height values was done using non-linear squares model. We used the best equation according to @Adameetal2008MixedNonlinear

$$h = 1.3 + a*\exp(b/dbh)$$ 

## Model height-diameter 
```{r}
# see pag. 391 from @PommereningGrabarnik2019IndividualbasedMethods
# See @Adameetal2008MixedNonlinear for equations. The best equation is 
# h ~ 1.3 + a*e^(b/D)
# start values from @Adameetal2008MixedNonlinear

# Remove data withouth dbh 
df_model <- tree %>% 
  filter(sp == "Qpyr") %>% 
  filter(!is.na(h))

# NonLinear Least Squares
m <- nls(h ~ 1.3 + a * exp(b / dbh),
         data = df_model, 
         start = list(a = 15, b = -10), trace = TRUE)
```

```{r, echo = FALSE}
tidy(m) %>% knitr::kable()
```

```{r, echo = FALSE}
glance(m) %>% knitr::kable()
```

```{r, echo = FALSE}
ggplot(broom::augment(m), aes(dbh, h)) +
  geom_point() +
  geom_line(aes(y = .fitted), colour = "red", size=1) +
  theme_bw()
```


Compute the estimate values 

```{r}
tree %<>% 
  mutate(h = ifelse(
    sp == "Qpyr" & hval == "est",
    predict(m, list(dbh = dbh)),
    h)) 

# (1.3 + coef(m)[1]*exp(coef(m)[2]/dbh))

```


```{r, echo = FALSE}
ggplot(tree, aes(dbh, h, colour=hval)) +
  geom_point() +
  # geom_line(broom::augment(m), aes(y = .fitted), colour = "red", size=1) +
  theme_bw()
```

Export data

```{r}
write_csv(tree, here::here("data/tree_data_full.csv"))
```

# References 