---
title: "Prepare Data from Forest Inventories"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r, message=FALSE, warning=FALSE}
source("./load_pkgs.R")
```


# MIGRAME 

We downloaded the DarwinCore Archive (`.zip` file) of our dataset from GBIF ([doi: 10.15470/orboj4](https://doi.org/10.15470/orboj4)). Then, we use the `finch` package [@finch] to process the Darwin Core Archive and load the datasets. 

```{r}
# x <- dwca_read("https://ipt.gbif.es/archive.do?r=migrame")
# 
# mig_occ <- read_delim(x$data[1], delim = "\t")
# mig_mof <- read_delim(x$data[2], delim = "\t")

mig_occ <- read_delim(here::here("raw_data/migrame/dwca-migrame-v1.8/occurrence.txt"), delim = "\t")
mig_mof <- read_delim(here::here("raw_data/migrame/dwca-migrame-v1.8/measurementorfact.txt"), delim = "\t")


# Get transect data 
# Transect data comes from Supplementary of https://doi.org/10.3897/phytokeys.56.5482 

# Table S1. Information about transects of the project. Elevation in m a.s.l.. 
# Type: AM = Altitudinal migration; FO = Forest; MH = Marginal Habitat. 
# Subtype: 
#   AC-e = Abandoned Cropland: edge; AC-i = Abandoned Cropland: inside; 
#   Pp-e = Pine plantations: edge; Pp-i: Pine plantations: inside; 
#   TE = Treeline Ecotone. 
# Locality: CA = Robledal de Cáñar; SJ = Robledal de San Juan.

mig_transectos <- read.table(here::here("raw_data/migrame/appendix_transects.csv"))
```


### Selección de datos

- Transectos realizados dentro del robledal

```{r}
fo <- mig_transectos %>% 
  filter(type == "FO") %>% as.data.frame()


# Prepare measurements
g <- mig_mof %>% dplyr::select(id, measurementType, measurementValue) %>% 
  spread(measurementType, measurementValue) %>% 
  rename(dbh = `diameter size`, h = `tree height`)

mig <- g %>% inner_join(mig_occ, by = "id") %>% 
  mutate(loc = case_when(
             locality == "Robledal de San Juan. Barranco de San Juan" ~ "SJ",
             locality == "Robledal de Cañar. Loma de Cañar" ~ "CA")) %>% 
  dplyr::select(id, dbh, h, eventDate, catalogNumber, loc, scientificName) %>% 
  separate(catalogNumber, c(NA, "tr", NA), sep ="-") %>% 
  filter(tr %in% unique(fo$name)) %>% 
  mutate(sp = case_when(
    scientificName == "Quercus pyrenaica Willd." ~ "Qpyr",
    scientificName == "Quercus ilex L. subsp. ballota" ~ "Qilex"
  ))

write_csv(mig, here::here("data/df_mig.csv"))

migData <- mig %>% 
  mutate(h = h/100, 
         project = "migrame") %>% 
  dplyr::select(code = tr, sp, h, dbh, project)

code sp h dbh 
# Read spatial info 

mig_spa <- rgdal::readOGR(dsn = here::here("/raw_data/geoinfo"), 
                   layer = "mig_transectos_polygon", 
                   verbose = TRUE, encoding = "UTF-8")

# Select transects and variables
mig_spaFO <- subset(mig_spa, nombre %in% unique(fo$name))
mig_spaFO <- mig_spaFO[, c("nombre", "fecha")]
names(mig_spaFO) <- c("code", "date")
```


# Dendro SN 

* Data from Pérez-Luque et al. (Submitted to *Ecosystems*).
* 50 target trees were cored for dendrochronological analysis
* Stand competition of target trees was assessed by recording distance, azimuth, DBH, species and total height of all neighboring living trees with DBH > 7.5 cm within a circular plot of 10 m radius.

```{r}
# Read spatial info 
dendrosn_spa <- rgdal::readOGR(dsn = here::here("/raw_data/geoinfo"), 
                   layer = "dendro_sn_polygon", 
                   verbose = TRUE, encoding = "UTF-8")

dendrosn_spa <- dendrosn_spa[, c("name", "cmt")]

dendrosn_spa@data$date <- parse_date(str_sub(dendrosn_spa@data$cmt, end=-10))
dendrosn_spa <- dendrosn_spa[, c("name", "date")]
names(dendrosn_spa)[1] <- "code"

dendrosn_Data <- read_csv(here::here("raw_data/dendro_sn/dendro_competence.csv")) %>% 
  dplyr::select(code = id_focal, sp, h = height_cm, perim_mm) %>% 
  filter(code != "Fresno") %>% 
  mutate(sp = case_when(
    sp == "Focal" ~ "Qpyr",
    TRUE ~ as.character(sp))) %>% 
  mutate(h = h / 100, # as meter
         dbh = round((perim_mm / 10)/pi,2), 
         project = "dendro_sn") %>% 
  dplyr::select(-perim_mm)

``` 


# Dendro LIFE

* Data from monitoring dendro LIFE-ADAPTAMED
* Several plots in Pyrenean oaks forest with variable size 
* Distance, azimuth, DBH, species and height of all living trees within a circular plot of variable radius were registered. 

```{r}
# Read spatial info 
dendrolife_spa <- rgdal::readOGR(dsn = here::here("/raw_data/geoinfo"), 
                   layer = "dendro_life_polygon", 
                   verbose = TRUE, encoding = "UTF-8")
dendrolife_spa <- dendrolife_spa[, c("code", "date")]
dendrolife_spa@data$date <- parse_date(dendrolife_spa@data$date)

dendrolife_Data <- read_csv(here::here("raw_data/dendro_life/dendro_life.csv")) %>% 
  mutate(sp = case_when(
    specie == "Quercus pyrenaica" ~ "Qpyr", 
    TRUE ~ "Qilex"), 
    project = "dendro_life") %>% 
  dplyr::select(code = loc, sp, h = treeHeight_m, dbh = dbh1_cm, project)

```

# OBSNEV San Jeronimo 

* 9 parcelas en el robledal de San Jerónimo
* 3 réplicas x 3 tratamientos (Control / Moderado / Intenso)
  
  * Control: No actuación. Parcelas de 20 x 20 m. En ellas se toman los datos de 10 individuos (distancia al centro; rumbo; dbh; diametro basal; altura) y también se toman datos del resto de individuos (diámetro basal y dbh)
  
  * Moderada: Eliminación de pies secos/enfermos, y los incluidos en una agrupación (conjunto de robles que distan entre sí menos de 3 m.) y que tengan un diámetro basal < 15 cm. 
  
  * Intenso: idem moderada + incremento de corta hasta 30 % seleccionándose para ello los pies enfermos, dominados y/o excesivamente densos, eliminándose en este último caso alguno de los pies que estén más próximos. 

### Inconvenientes / DUDAS: 
* Solamente las parcelas control no fueron tratadas, por lo que tendríamos solamente 3 parcelas. 
* De las otras, siempre tendríamos en torno al centroide 10 árboles localizados (con todas sus medidas)
* De las parcelas control, solamente tenemos datos completos de 10 árboles. Del resto de los árboles de la parcela tenemos datos de diámetros. Podemos no utilizarlos o realizar una estimación de la altura a partir de ecuaciónes de regresión. 

```{r}
# Read spatial info 
obsnev_sjer <- rgdal::readOGR(dsn = here::here("/raw_data/geoinfo"), 
                   layer = "obsnev_sjeronimo_polygon",
                   verbose = TRUE, encoding = "UTF-8")
obsnev_sjer <- obsnev_sjer[, c("code", "fecha")]
names(obsnev_sjer)[2] <- "date"
obsnev_sjer@data$date <- parse_date(obsnev_sjer@data$date)
```

### SINFONEVADA

We downloaded the DarwinCore Archive (`.zip` file) of our dataset from GBIF ([doi: 10.15468/4gpr7e](https://doi.org/10.15468/4gpr7e)). Then, we use the `finch` package [@finch] to process the Darwin Core Archive and load the datasets. 

```{r}
# sinfodwca  <- dwca_read("https://ipt.gbif.es/archive.do?r=sinfonevada&v=1.5")
# sinfo_occ <- read_delim(sinfodwca$data[1], delim = "\t")

sinfo_occ <- read_delim(here::here("raw_data/sinfonevada/dwca-sinfonevada-v1.5/occurrence.txt"), delim = "\t")

sinfo_plots <- sinfo_occ %>%
  separate(catalogNumber, c(NA,"id_parcela", NA, NA), sep = "-") %>% 
  mutate(id_parcela = as.numeric(id_parcela)) %>% 
  dplyr::select(id_parcela, decimalLatitude, decimalLongitude) %>% que()

sinfo_aux <- read_csv(here::here("raw_data/sinfonevada/parcelas_sinfo_qp.csv"))


sinfo_qp <- sinfo_plots %>% 
  inner_join(sinfo_aux, by="id_parcela")
  
sinfo_qp_spa <- SpatialPointsDataFrame(coords = sinfo_qp[,c("decimalLongitude","decimalLatitude")], 
                                       data = sinfo_qp, 
                                       proj4string = CRS("+init=epsg:4326"))

```


* Each inventory plot has three sampling ts: i) a forest inventory plot (20 × 20 m); ii) a 5-m radius subplot for the estimation of the regeneration; iii) and a 10-m radius subplot for species composition and abundance. Each live tree with a diameter at breast height (dbh) > 7.5 cm was tallied by species and dbh in the forest inventory plot. 

* Tenemos datos del centroide pero no del polígono. 


### CAMARATE
* Parcelas realizadas en la zona de CAMARATE especificamente para caracterizar la estructura


```{r}
# Read spatial info 
camarate <- rgdal::readOGR(dsn = here::here("/raw_data/geoinfo"), 
                   layer = "camarate_dasometrico_polygon",
                   verbose = TRUE, encoding = "UTF-8")

camarate@data$date <- parse_date(camarate@data$date)

# Data 
camarateData <- read_csv(here::here("raw_data/camarate/camarate_tree_data.csv")) %>% 
   mutate(sp = case_when(
    sp == "Quercus pyrenaica" ~ "Qpyr",
    sp == "Acer opalus granatensis" ~ "Aopa", 
    sp == "Sorbus aria" ~ "Saria", 
    TRUE ~ "Cmon"), 
    project = "camarate") %>% 
  dplyr::select(code = plot, sp, h = height, dbh = dbh, project)
```

* Eliminar > 16 m distancia en CAM_H2

# Unir capas 
```{r}
# Check projection and if not 4326 transform 

# CRS("+init=epsg:4326")
p <-projection(obsnev_sjer)
  
camarate <- spTransform(camarate, p)
mig_spaFO <- spTransform(mig_spaFO, p)
dendrosn_spa<- spTransform(dendrosn_spa, p)
dendrolife_spa<- spTransform(dendrolife_spa, p)


plotsQP <- rbind(dendrolife_spa, dendrosn_spa,
           mig_spaFO, camarate, obsnev_sjer,
           makeUniqueIDs = TRUE)  


# Add data 
dicc_plot <- read_csv(here::here("raw_data/dicc_plots.csv"))

plotsQP <- merge(plotsQP, dicc_plot, duplicateGeoms = T)


writeOGR(plotsQP, 
         dsn = here::here("/data/geoinfo"), 
         "plotsQP", driver="ESRI Shapefile", overwrite_layer = TRUE)

```


# Visualize plots and Q. pyrenaica forests 
* Read Q. pyrenaica forests 

```{r}
qp_sn <- rgdal::readOGR(dsn="/Users/ajpelu/Google Drive/_phd/qpyr_distribution/data_raw/geoinfo/",
                    layer = 'q_pyr_sn_4326', verbose = TRUE, encoding = "UTF-8")

qp_sn25 <- rgdal::readOGR(dsn="/Users/ajpelu/Google Drive/_phd/qpyr_distribution/data_raw/geoinfo/",
                    layer = 'q_pyr_sn25830', verbose = TRUE, encoding = "UTF-8")

qpR <- spTransform(qp_sn25, CRS("+init=epsg:4326"))

mapview::mapview(qp_sn25)
```

# Generar datos 
```{r}
tree <-  bind_rows(list(migData, dendrolife_Data, dendrosn_Data, camarateData))

ggplot(tree, aes(x=dbh, y=h)) + geom_point()

```


```{r}
# see pag. 391 from @PommereningGrabarnik2019IndividualbasedMethods
# See @Adameetal2008MixedNonlinear for equations. The best equation is 
# h ~ 1.3 + a*e^(b/D)
# start values from @Adameetal2008MixedNonlinear

# Remove data withouth dbh 

treeqp <- tree %>% 
  filter(!is.na(dbh)) %>% 
  filter(!is.na(h))

nlsqp <- nls(h ~ 1.3 + a * exp(b / dbh),
             data = treeqp, 
             start = list(a = 15, b = -10), trace = TRUE)

# Create new data by each 0.5 cm 
nd <- data.frame(
  dbh = seq(0, 140, by = 0.5)) 

summary(nlsqp)

plot(treeqp$h ~ treeqp$dbh, pch=19, col="gray40", cex =.5) 
# newdata <- seq(0, 120, length = 1200)
# lines(nd, predict(nlsqp, list(dbh = newdata)), col = "green", lwd = 2)

# http://sia.webpopix.org/nonlinearRegression.html 
# propagate pkg 
prop <- predictNLS(nlsqp, newdata = nd)

ci_nlsqp <- prop$summary
write_csv(ci_nlsqp, here::here("data/conf_intervals_qp.csv"))


# vas por aquí 

p <- data.frame(lc = prop$summary$`Prop.2.5%`, 
                uc = prop$summary$`Prop.97.5%`)


p <- cbind(nd, p)
lines(p$dbh, p$lc, col = "red")
lines(p$dbh, p$uc, col = "red")
qpboot <- nlsBoot(nlsqp, niter = 999)
plot(qpboot)
summary(qpboot)


nd <- data.frame(
  dbh = seq(0, 120, length = 1200)) 

nd <- nd %>% 
  mutate(
    lci = 1.3 + 15.42403 * exp(-13.18342 / dbh),
  uci = 1.3 + 16.23157 * exp(-12.09951/ dbh)
)


confint2(nlsqp)



coef(nlsqp)


```


