---
title: "Prepare Data from Forest Inventories"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r, message=FALSE, warning=FALSE}
source(here::here("load_pkgs.R"))
```


# MIGRAME 

We downloaded the DarwinCore Archive (`.zip` file) of our dataset from GBIF ([doi: 10.15470/orboj4](https://doi.org/10.15470/orboj4)). Then, we use the `finch` package [@finch] to process the Darwin Core Archive and load the datasets. 

```{r}
# x <- dwca_read("https://ipt.gbif.es/archive.do?r=migrame")
# 
# mig_occ <- read_delim(x$data[1], delim = "\t")
# mig_mof <- read_delim(x$data[2], delim = "\t")

mig_occ <- read_delim(here::here("raw_data/migrame/dwca-migrame-v1.8/occurrence.txt"), delim = "\t")
mig_mof <- read_delim(here::here("raw_data/migrame/dwca-migrame-v1.8/measurementorfact.txt"), delim = "\t")


# Get transect data 
# Transect data comes from Supplementary of https://doi.org/10.3897/phytokeys.56.5482 

# Table S1. Information about transects of the project. Elevation in m a.s.l.. 
# Type: AM = Altitudinal migration; FO = Forest; MH = Marginal Habitat. 
# Subtype: 
#   AC-e = Abandoned Cropland: edge; AC-i = Abandoned Cropland: inside; 
#   Pp-e = Pine plantations: edge; Pp-i: Pine plantations: inside; 
#   TE = Treeline Ecotone. 
# Locality: CA = Robledal de Cáñar; SJ = Robledal de San Juan.

mig_transectos <- read.table(here::here("raw_data/migrame/appendix_transects.csv"))

# Seleccionar datos de transectos dentro del robledal 

fo <- mig_transectos %>% 
  filter(type == "FO") %>% as.data.frame()

# Prepare measurements
g <- mig_mof %>% dplyr::select(id, measurementType, measurementValue) %>% 
  spread(measurementType, measurementValue) %>% 
  rename(dbh = `diameter size`, h = `tree height`)

mig <- g %>% inner_join(mig_occ, by = "id") %>% 
  mutate(loc = case_when(
             locality == "Robledal de San Juan. Barranco de San Juan" ~ "SJ",
             locality == "Robledal de Cañar. Loma de Cañar" ~ "CA")) %>% 
  dplyr::select(id, dbh, h, eventDate, catalogNumber, loc, scientificName) %>% 
  separate(catalogNumber, c(NA, "tr", NA), sep ="-") %>% 
  filter(tr %in% unique(fo$name)) %>% 
  mutate(sp = case_when(
    scientificName == "Quercus pyrenaica Willd." ~ "Qpyr",
    scientificName == "Quercus ilex L. subsp. ballota" ~ "Qilex"
  ))


mig %<>% 
  mutate(h = h/100, 
         hval = "field",
         project = "migrame") %>% 
  dplyr::select(code = tr, sp, dbh, h, hval, project)


# Filter data 
# cuantos ind sin diámetro? 
mig %>% filter(is.na(dbh)) %>% group_by(sp) %>% count()

# Maxima h 
mig %>% filter(is.na(dbh)) %>% summarise(hmax = max(h))

# Estimar datos de diámetro para valores h < 2.1 
## ploteo 
mig %>% 
  filter(!is.na(dbh)) %>% 
  filter(sp == "Qpyr") %>% 
  filter(h < 2.1) %>% 
  ggplot(aes(x=dbh, y = h)) + 
  geom_point() +
  geom_smooth()

##  Elimino outliers: aquellos valores de h < 2.1 con dbh > 10 
mig %<>% filter(!(dbh %in% c(12,15) & h < 2.1))
               
## Elimino datos con dbh = 0                
mig %<>% filter(!(dbh == 0) | is.na(dbh))

# Creo subset de datos con 
mig_h2 <- mig %>% 
  filter(sp == "Qpyr") %>% 
  filter(!is.na(dbh) & h < 2.1)

mig_h2 %>% 
 ggplot(aes(x=dbh, y = h)) + 
  geom_point() +
  geom_smooth()
 

# Computar modelo de dbh para los datos de h < 2.1
m_dbh <- nls(dbh ~ a + b * exp(h),
         data = mig_h2, 
         start = list(a=0.1, b=0.1), trace = TRUE)

mig_h2 %>% 
 ggplot(aes(y=dbh, x = h)) + 
  geom_point() +
  geom_smooth(method="nls", 
              formula=y~a+b*exp(x), 
              method.args = list(start=c(a=0.5,b=0.45)),
              se = FALSE)

# Estimar valores de dbh para datos de h < 2.1 
mig %<>% 
  mutate(dval = case_when(
    is.na(dbh) ~ "est", 
    TRUE ~ "field")) %>% 
  mutate(dbh = 
        ifelse(is.na(dbh) & sp == "Qpyr", 
             round((coef(m_dbh)[1] + coef(m_dbh)[2] * exp(h)), 2),
             dbh))
  












migData %>% 
  filter(!is.na(dbh)) %>% 
  filter(sp == "Qpyr") %>% 
  filter(h < 2.1) %>% 
 ggplot(aes(x=h, y = dbh)) + 
  geom_point() +
  geom_smooth()









migData %>% 





# Read spatial info 
mig_spa <- rgdal::readOGR(dsn = here::here("/raw_data/geoinfo"), 
                   layer = "mig_transectos_polygon", 
                   verbose = TRUE, encoding = "UTF-8")

# Select transects and variables
mig_spaFO <- subset(mig_spa, nombre %in% unique(fo$name))
mig_spaFO <- mig_spaFO[, c("nombre", "fecha")]
names(mig_spaFO) <- c("code", "date")
```

# Dendro SN 

* Data from Pérez-Luque et al. (Submitted to *Ecosystems*).
* 50 target trees were cored for dendrochronological analysis
* Stand competition of target trees was assessed by recording distance, azimuth, DBH, species and total height of all neighboring living trees with DBH > 7.5 cm within a circular plot of 10 m radius.

```{r}
# Read spatial info 
dendrosn_spa <- rgdal::readOGR(dsn = here::here("/raw_data/geoinfo"), 
                   layer = "dendro_sn_polygon", 
                   verbose = TRUE, encoding = "UTF-8")

dendrosn_spa <- dendrosn_spa[, c("name", "cmt")]

dendrosn_spa@data$date <- parse_date(str_sub(dendrosn_spa@data$cmt, end=-10))
dendrosn_spa <- dendrosn_spa[, c("name", "date")]
names(dendrosn_spa)[1] <- "code"

dendrosn_Data <- read_csv(here::here("raw_data/dendro_sn/dendro_competence.csv")) %>% 
  dplyr::select(code = id_focal, sp, perim_mm, h = height_cm) %>% 
  filter(code != "Fresno") %>% 
  mutate(sp = case_when(
    sp == "Focal" ~ "Qpyr",
    TRUE ~ as.character(sp))) %>% 
  mutate(dbh = round((perim_mm / 10)/pi,2),
         h = h / 100, # as meter
         hval = "field",
         project = "dendro_sn") %>% 
  dplyr::select(-perim_mm)

``` 


# Dendro LIFE

* Data from monitoring dendro LIFE-ADAPTAMED
* Several plots in Pyrenean oaks forest with variable size 
* Distance, azimuth, DBH, species and height of all living trees within a circular plot of variable radius were registered. 

```{r}
# Read spatial info 
dendrolife_spa <- rgdal::readOGR(dsn = here::here("/raw_data/geoinfo"), 
                   layer = "dendro_life_polygon", 
                   verbose = TRUE, encoding = "UTF-8")
dendrolife_spa <- dendrolife_spa[, c("code", "date")]
dendrolife_spa@data$date <- parse_date(dendrolife_spa@data$date)

dendrolife_Data <- read_csv(here::here("raw_data/dendro_life/dendro_life.csv")) %>% 
  mutate(sp = case_when(
    specie == "Quercus pyrenaica" ~ "Qpyr", 
    TRUE ~ "Qilex"), 
    hval = "field",
    project = "dendro_life") %>% 
  dplyr::select(code = loc, sp, dbh = dbh1_cm, h = treeHeight_m, hval, project)

```


# Robledal LIFE

* Parcelas de CANAR = robledal puro. PORTUGOS = robledal-encinar
* Solamente 5 árboles tipo por plot 
* Estimar h por ecuacion

```{r}
# list ods files 
ods_file_names <- here::here("raw_data/robledal_life/") %>%
  list.files() %>%
  .[str_detect(., ".ods")] 

# Read tree data 
df_dbh <- ods_file_names %>% 
  purrr::map_dfr(function(file_name){ # iterate through each file name
    daso <- read_ods(paste0(here::here("raw_data/robledal_life/"), file_name),
                          sheet = "1_DASOMETRICO") %>%
      as_tibble(.name_repair = "unique") %>% # Name variable col 7
      mutate(code = str_remove(file_name, "_c1_forestal.ods"))
    }) %>% 
  filter(is.na(`...7`)) %>% 
  dplyr::select(-CUADRANTE, sp = ESPECIE, -`...7`, 
                dbh1 = "Dnor (cm) 1", dbh2 = "Dnor (cm) 2", 
                dbase1 ="Dbas (cm) 1", dbase2 = "Dbas (cm) 2")
      

df_aux <- df_dbh %>% 
   mutate(sp = case_when(
    sp == "Quercus pyrenaica" ~ "Qpyr",
    sp == "Quercus ilex" ~ "Qilex"),
    h = NA, hval = "est", project = "robledal_life") %>% 
  rowwise() %>% 
  mutate(dbh = max(c(dbh1, dbh2))) %>% 
  dplyr::select(code, sp, dbh, h, hval, project) %>% 
  filter(str_detect(code, "CAN"))
  

    
# Read tipo data 
df_tipo <- ods_file_names %>% 
  purrr::map_dfr(function(file_name){ 
    daso <- read_ods(paste0(here::here("raw_data/robledal_life/"), file_name),
                          sheet = "2_EJEMPLARES_TIPO") %>%
      as_tibble(.name_repair = "unique") %>% # Name variable col 7
      mutate(code = str_remove(file_name, "_c1_forestal.ods"))
    }) %>% 
   dplyr::select(sp = Especie, h = "Altura (m)", 
                dbh1 = "D.nor (cm) 1", dbh2 = "D.nor (cm) 2", 
                dbase1 ="D.bas (cm) 1", dbase2 = "D.bas (cm) 2", 
                code) 

df_auxtipo <- df_tipo %>% 
   mutate(sp = case_when(
    sp == "Quercus pyrenaica" ~ "Qpyr"),
    hval = "field", project = "robledal_life") %>% 
  rowwise() %>% 
  mutate(dbh = max(c(dbh1, dbh2))) %>% 
  dplyr::select(code, sp, dbh, h, hval, project) %>% 
  filter(str_detect(code, "CAN"))

robledal_lifeData <- df_aux %>% rbind(df_auxtipo)
```

# OBSNEV San Jeronimo 

* 9 parcelas en el robledal de San Jerónimo
* 3 réplicas x 3 tratamientos (Control / Moderado / Intenso)
  
  * Control: No actuación. Parcelas de 20 x 20 m. En ellas se toman los datos de 10 individuos (distancia al centro; rumbo; dbh; diametro basal; altura) y también se toman datos del resto de individuos (diámetro basal y dbh)
  
  * Moderada: Eliminación de pies secos/enfermos, y los incluidos en una agrupación (conjunto de robles que distan entre sí menos de 3 m.) y que tengan un diámetro basal < 15 cm. 
  
  * Intenso: idem moderada + incremento de corta hasta 30 % seleccionándose para ello los pies enfermos, dominados y/o excesivamente densos, eliminándose en este último caso alguno de los pies que estén más próximos. 

### Inconvenientes / DUDAS: 
* Solamente las parcelas control no fueron tratadas, por lo que tendríamos solamente 3 parcelas. 
* De las otras, siempre tendríamos en torno al centroide 10 árboles localizados (con todas sus medidas)
* De las parcelas control, solamente tenemos datos completos de 10 árboles. Del resto de los árboles de la parcela tenemos datos de diámetros. Podemos no utilizarlos o realizar una estimación de la altura a partir de ecuaciónes de regresión. 

```{r}
# Read spatial info 
obsnev_sjer <- rgdal::readOGR(dsn = here::here("/raw_data/geoinfo"), 
                   layer = "obsnev_sjeronimo_polygon",
                   verbose = TRUE, encoding = "UTF-8")
obsnev_sjer <- obsnev_sjer[, c("code", "fecha")]
names(obsnev_sjer)[2] <- "date"
obsnev_sjer@data$date <- parse_date(obsnev_sjer@data$date)



# Data
j <- readxl::read_xlsx(
  here::here("raw_data/obs_sanjeronimo/san_jeronimo_cleaned.xlsx")) %>% 
  rowwise() %>% 
  mutate(dbh = max(c(Dn1, Dn2)),
         project = "obsnev_sjer", 
         sp = recode(especie, "Quercus pyrenaica" = "Qpyr")) 
  

# Get only Data of "tipo" trees from all plots
j_tipo <- j %>% 
  filter(!is.na(tipo)) %>%
  rowwise() %>% 
  mutate(h = max(c(h1, h2, htot), na.rm = TRUE)) %>%
  filter(h != -Inf) %>% 
  mutate(hval = "field") %>% 
  dplyr::select(code, sp, dbh, h, hval, project) 


# Get other data 
j_all <- j %>% 
  filter(is.na(tipo)) %>% 
  mutate(h = NA, hval = "est") %>% 
  dplyr::select(code, sp, dbh, h, hval, project)
  

obsnev_sjerData <- j_all %>% rbind(j_tipo)
  
```

### SINFONEVADA

We downloaded the DarwinCore Archive (`.zip` file) of our dataset from GBIF ([doi: 10.15468/4gpr7e](https://doi.org/10.15468/4gpr7e)). Then, we use the `finch` package [@finch] to process the Darwin Core Archive and load the datasets. 

```{r}
# sinfodwca  <- dwca_read("https://ipt.gbif.es/archive.do?r=sinfonevada&v=1.5")
# sinfo_occ <- read_delim(sinfodwca$data[1], delim = "\t")

sinfo_occ <- read_delim(here::here("raw_data/sinfonevada/dwca-sinfonevada-v1.5/occurrence.txt"), delim = "\t")

sinfo_plots <- sinfo_occ %>%
  separate(catalogNumber, c(NA,"id_parcela", NA, NA), sep = "-") %>% 
  mutate(id_parcela = as.numeric(id_parcela)) %>% 
  dplyr::select(id_parcela, decimalLatitude, decimalLongitude) %>% que()

sinfo_aux <- read_csv(here::here("raw_data/sinfonevada/parcelas_sinfo_qp.csv"))


sinfo_qp <- sinfo_plots %>% 
  inner_join(sinfo_aux, by="id_parcela")
  
sinfo_qp_spa <- SpatialPointsDataFrame(coords = sinfo_qp[,c("decimalLongitude","decimalLatitude")], 
                                       data = sinfo_qp, 
                                       proj4string = CRS("+init=epsg:4326"))

```


* Each inventory plot has three sampling ts: i) a forest inventory plot (20 × 20 m); ii) a 5-m radius subplot for the estimation of the regeneration; iii) and a 10-m radius subplot for species composition and abundance. Each live tree with a diameter at breast height (dbh) > 7.5 cm was tallied by species and dbh in the forest inventory plot. 

* Tenemos datos del centroide pero no del polígono. 


### CAMARATE
* Parcelas realizadas en la zona de CAMARATE especificamente para caracterizar la estructura


```{r}
# Read spatial info 
camarate <- rgdal::readOGR(dsn = here::here("/raw_data/geoinfo"), 
                   layer = "camarate_dasometrico_polygon",
                   verbose = TRUE, encoding = "UTF-8")

camarate@data$date <- parse_date(camarate@data$date)

# Data 
camarateData <- read_csv(here::here("raw_data/camarate/camarate_tree_data.csv")) %>% 
  filter(dis < 16) %>% 
   mutate(sp = case_when(
    sp == "Quercus pyrenaica" ~ "Qpyr",
    sp == "Acer opalus granatensis" ~ "Aopa", 
    sp == "Sorbus aria" ~ "Saria", 
    TRUE ~ "Cmon"), 
    hval = "field",
    project = "camarate") %>% 
  dplyr::select(code = plot, sp, dbh = dbh, h = height, hval, project)
```

* Eliminar > 16 m distancia en CAM_H2

# Unir capas 
```{r}
# Check projection and if not 4326 transform 

# CRS("+init=epsg:4326")
p <-projection(obsnev_sjer)
  
camarate <- spTransform(camarate, p)
mig_spaFO <- spTransform(mig_spaFO, p)
dendrosn_spa<- spTransform(dendrosn_spa, p)
dendrolife_spa<- spTransform(dendrolife_spa, p)


plotsQP <- rbind(dendrolife_spa, dendrosn_spa,
           mig_spaFO, camarate, obsnev_sjer,
           makeUniqueIDs = TRUE)  


# Add data 
dicc_plot <- read_csv(here::here("raw_data/dicc_plots.csv"))

plotsQP <- merge(plotsQP, dicc_plot, by.x ="code", by.y="original_code")


writeOGR(plotsQP, 
         dsn = here::here("/data/geoinfo"), 
         "plotsQP", driver="ESRI Shapefile", overwrite_layer = TRUE)

```


# Visualize plots and Q. pyrenaica forests 
* Read Q. pyrenaica forests 

```{r}
qp_sn <- rgdal::readOGR(dsn="/Users/ajpelu/Google Drive/_phd/qpyr_distribution/data_raw/geoinfo/",
                    layer = 'q_pyr_sn_4326', verbose = TRUE, encoding = "UTF-8")

qp_sn25 <- rgdal::readOGR(dsn="/Users/ajpelu/Google Drive/_phd/qpyr_distribution/data_raw/geoinfo/",
                    layer = 'q_pyr_sn25830', verbose = TRUE, encoding = "UTF-8")

qpR <- spTransform(qp_sn25, CRS("+init=epsg:4326"))

mapview::mapview(qp_sn25)
```

# Generar datos 
```{r}
tree <-  bind_rows(
  list(migData, dendrolife_Data, dendrosn_Data, camarateData, obsnev_sjerData, robledal_lifeData))

write_csv(tree, here::here("data/tree_data.csv"))

```



